---
title: "Fun with animated plotting in R"
output: 
  learnr::tutorial:
     progressive: false
runtime: shiny_prerendered
description: >
  Animated plotting in R with 'animate'
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


## Introduction

Welcome to "Fun with animated plotting in R with 'animate'"!

In this series of articles, we will do some exercises with animated plotting in R and have some fun playing with art, coding and mathematics.


### The R package 'animate'

'animate' is ...

#### Set up a device in the R Markdown Document

```{r two-plus-two, exercise=TRUE}
# Load and set up the device
library(animate)
device <- animate$new(500, 500, virtual = TRUE)
attach(device)

# Create some data
id <- new_id(1:10)
s <- 1:10 * 2 * pi / 10
s2 <- sample(s)

# Make an 'animate' plot
par(xlim = c(-2.5, 2.5), ylim = c(-2.5, 2.5))
plot(2*sin(s), 2*cos(s), id = id)
points(sin(s2), cos(s2), id = id, transition = list(duration = 2000))

# Render the plot in-line. This line is needed if you use 'animate' in a code chunk of an R Markdown Document.
rmd_animate(device, click_to_play(start = 3))  # begin the plot at the third frame
```






## Day 1: Mathematical Rose

### Set up the device

```{r day-2-device-setup, exercise=T, message=F, warning=F}
library(animate)
device <- animate$new(600, 600, virtual = TRUE)
attach(device)
set_max_stacksize(0)


rose <- function(theta, a = 1, k = 3) {
    # `a` controls the size, `k` controls the shape
    list(x = a * cos(k * theta) * cos(theta),
         y = a * cos(k * theta) * sin(theta))
}

# k = p / q, where p and q should be coprime, e.g. 1/3, 2/7, not 2/6, 3/6.
# If p and q are not coprime, then the rose will be drawn more than once.
p <- 2
q <- 7


is_odd <- function(x) x %% 2 == 1
period <- ifelse(is_odd(p) && is_odd(q), pi * q, 2 * pi * q)

# Compute the rose with the parameters `p` and `q` for time=0 to time=`period`
time <- seq(from = 0, to = period, length.out = 400)  # 400 time steps
pts <- rose(time, a = 1, k = p / q)


par(xlim = extendrange(pts$x), ylim = extendrange(pts$y))
for (step in seq_along(time)) {
    lines(pts$x[1:step], pts$y[1:step], id = "line-1")
    points(pts$x[step], pts$y[step], id = "point-1")
    # Sys.sleep(0.01)
}
rmd_animate(device, click_to_loop(start = 3, wait = 10))
```


### Implement the rose function

Some calculation is needed to work out the number of time steps required to get to the end of the drawing of the rose. Assuming $p$ and $q$ are coprime, then the period is $\pi q$ if both $p$ and $q$ are odd, and $2 \pi q$ otherwise.

### Plot the rose 

### Clean up 







## Day 2

### Perlin noise

```{r perlin-noise, exercise=TRUE, exercise.lines = 5}
# smooth_step <- function(x, edge_0, edge_1) {
#   x <- clamp((x - edge_0) / (edge_1 - edge_0), 0, 1)
#   x * x * (3 - 2*x)
# }
# 
# clamp <- function(x, lower_limit, upper_limit) {
#   if (x < lower_limit) return(lower_limit)
#   if (x > upper_limit) return(upper_limit)
#   x
# }
# 
# general_smooth_step <- function(x, m) {
#   x <- clamp(x, 0, 1)
#   result <- 0
#   for (n in 0:m) {
#     result <- result + choose(-m-1, n) * choose(2*m+1, m-n) * x^(m+n+1)
#   }
#   result
# }
# 
# perlin_noise <- function() {
#   
# }
# 
# runif()
```








